### 2016-06-20 config/styles.inc.tex
Last figure?
Some improvements in figures, consistency
Thicker lines in MC figures

@@

%% MC LRM
\pgfplotsset{mcrmse/.style={dotted}}
\pgfplotsset{mcbias/.style={solid}}
\pgfplotsset{mcvar/.style={dashed}}

>>>>

\pgfplotsset{individualSamples/.append style={mark size=0.5pt,opacity=0.7,draw=none,solid,only marks}}
\pgfplotsset{boxplotBox/.append style={area legend,solid,draw=none,opacity=0.7}}
\pgfplotsset{boxplotBoxInit/.append style={area legend,solid,draw=none,opacity=0.15}}
\pgfplotsset{boxplotQuantiles/.append style={solid}}

@@

%% MC LRM
\pgfplotsset{mcline/.append style={line width=0.75pt}}
\pgfplotsset{mcrmse/.append style={mcline, dotted}}
\pgfplotsset{mcbias/.append style={mcline, solid}}
\pgfplotsset{mcvar/.append style={mcline, dashed}}
\pgfplotsset{mcnoise/.append style={mcline, solid}}
\pgfplotsset{mcpress/.append style={mcline, solid}}
